|

### 2025-01-29 doc/paper.qmd
prep

1. To ensure a smooth and conflict-free process, I handle the WSCP/Datastream workflow separately, preventing potential interference with the CRSP/Compustat pull process and improving debugging efficiency. Although a unified pull/prepare/do_analysis file for all databases would be ideal and streamline management, the large-scale nature of the extracted datasets is chosen for modular approach. Therefore, I isolate the data pull for @sec-task3 into `pull_wrds_data-wscp`, thus reducing complicated dependencies across tasks. To maintain structural consistency, I implement same approach for subsequent steps, including data preparation and analysis.

@@

**Step 2: Data Preparation**

>>>>

1. To ensure a smooth and conflict-free process, I handle the WSCP/Datastream workflow separately, preventing potential interference with the CRSP/Compustat pull process and improving debugging efficiency. Although a unified pull/prepare/do_analysis file for all databases would be ideal and streamline management, the large-scale nature of the extracted datasets demands modular approach. Therefore, I isolate the workflow for @sec-task3 into working files `...-wscp`, thus reducing complicated dependencies across tasks.

@@

**Step 2: Data Preparation**  
First, I merged Worldscope stock data with the linking table using `code` as unique identifier, resulting in 747,760 observations. This merged dataset was then joined with Datastream daily stock data using `infocode`, producing a final dataset with 10,249,737 observations.
